---
title: "Age differences in Hollywood movies"
date: "2023-02-27"
format: gfm
output-file: README.md
execute::echo: true
knitr::opts_chunk:
    comment: "#>"
    message: false
    error: false
    collapse: true
fig-show: true
df-print: kable
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringr)
library(styler)

?styler

theme_set(theme_light())

tuesdata <- tidytuesdayR::tt_load(2023, week = 7)

age_gaps <- tuesdata$age_gaps

# age_gaps
```

# PART I. Age differences between characters in movies directed by Woody Allen.

```{r}
age_gaps |>
  filter(director == "Woody Allen") |>
  select(movie_name, release_year, age_difference, couple_number) |>
  arrange(desc(release_year))
```

**1. What is the range of age differences between characters in Woody Allen's movies?**

```{r}
age_gaps |>
  filter(director == "Woody Allen") |>
  select(age_difference) |>
  range()
```

The range of age differences is 4-40 years.

2.  **What is the mean age difference between characters in Woody Allen's movies across the years?**

```{r}
age_gaps |>
  filter(director == "Woody Allen") |>
  select(movie_name, release_year, age_difference, couple_number) |>
  count(movie_name, sort = TRUE)
```

Out of 20 movies directed by Woody Allen in this data set, 6 movies have entries detailing the age difference between more than one couple. Therefore, it would be helpful to know the mean age difference of all couples in each movie to make data visualisation easier.

```{r}
age_difference_WA_movies <-
  age_gaps |>
  filter(director == "Woody Allen") |>
  select(movie_name, release_year, age_difference, couple_number) |>
  arrange(desc(release_year))

age_difference_WA_movies
```

```{r}
character_mean_age_difference_WA_movies <-
  age_difference_WA_movies |>
  group_by(movie_name) |>
  summarize(
    mean_age_difference =
      round(mean(age_difference, digits = 0))
  ) |>
  arrange(desc(mean_age_difference))

character_mean_age_difference_WA_movies
```

<!-- Checking if these calculations are correct by manually calculating two examples. -->

<!-- mighty_aphrodite_mean_age_difference <-  -->

<!-- sum((32 + 31 + 19)/3) |>  -->

<!-- round(digits = 0) |> -->

<!-- print() -->

<!-- character_mean_age_difference_WA_movies |>  -->

<!-- filter(movie_name =="Mighty Aphrodite") -->

<!-- The mean age difference between the three couples in the "Mighty Aphrodite" movie is 27 years according to the manual calculation. -->

3.  **Visualising how age difference between characters in Woody Allen's movies have fluctuated over the years.**

<!-- character_mean_age_difference_WA_movies  -->

<!-- The data frame showing all mean age difference scores for all WA movies -->

```{r}
age_difference_WA_movies_clean <-
  age_difference_WA_movies |>
  select(-age_difference, -couple_number) |>
  distinct(movie_name, release_year)

age_difference_WA_movies_clean
```

This table shows all Woody Allen's movie names and their release years. It would be helpful to merge it with one of the earlier tables showing mean age difference scores for all of these movies.

<!-- Now joining these two data frames together. -->

```{r}
WA_character_age_difference <-
  merge(
    x = character_mean_age_difference_WA_movies,
    y = age_difference_WA_movies_clean,
    by = "movie_name"
  ) |>
  arrange(desc(release_year))

WA_character_age_difference
```

<!-- This data frame now includes all movie titles, their release year, and mean age difference between included couple characters. -->

Now it's possible to visualise the mean age difference between characters in Woody Allen's movies across the years.

```{r}
WA_mean_age_plot <-
  WA_character_age_difference |>
  ggplot(aes(release_year, mean_age_difference, colour = movie_name)) +
  geom_line() +
  geom_point(size = 3, show.legend = TRUE) +
  expand_limits(
    x = c(1970, 2020),
    y = c(0, 30)
  ) +
  labs(
    x = "Movie release year",
    y = "Mean age difference between love characters",
    title = "Age difference between love characters in Woody Allen's films (1977-2016) \nover the years",
    colour = "Movie name"
  )

WA_mean_age_plot
```
#PART II. Age differences in movies across the data set.

1. Which movies has the highest and the lowest age differences between love characters?

```{r}
highest_age_difference <- age_gaps |>
  select(movie_name, release_year, age_difference) |>
  head(10) |>
  arrange(desc(age_difference))

highest_age_difference
```

```{r}
highest_age_difference |>
  ggplot(aes(age_difference, movie_name, color = movie_name)) +
  geom_point(show.legend = TRUE) +
  expand_limits(x = c(35, 55)) +
  labs(
    x = "Age difference between characters",
    y = "Movie title",
    color = "Movie title",
    title = "10 movies with highest age difference\n between love characters"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, color = "red", face = "bold"))
```

```{r}
lowest_age_difference <-
  age_gaps |>
  select(movie_name, release_year, age_difference) |>
  tail(10)

lowest_age_difference
```
